---
output: github_document
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/muschellij2/leanpubr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/muschellij2/leanpubr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# leanpubr Package: 
The goal of `leanpubr` is to provide provides access to the 'Leanpub' 'API' <https://leanpub.com/help/api> for gathering information about publications and submissions to the 'Leanpub' platform.

## Installation

You can install `leanpubr` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("muschellij2/leanpubr")
```

## Setting the API key
The main thing you need to do is get an API key from Leanpub.  You can do this by visiting https://leanpub.com/user_dashboard/api_key if you are an author.  If you are not an author, I don't believe access to the API is possible.  You can pass this `api_key` to functions in Leanpub (almost all prefixed by `lp_`), or you can set the environmental variable `LEANPUB_API_KEY`.  You can set this in an interactive `R` session such as:

```r
Sys.setenv("LEANPUB_API_KEY" = "YOUR_KEY")
```

or put this in your `~/.Renviron`:

```r
LEANPUB_API_KEY = "YOUR_KEY"
```


## Example

You can use `lp_book_info` to get information about any book in Leanpub:

```{r, echo = FALSE}
Sys.setenv("LEANPUB_API_KEY" = "asdf")
```

```{r}
library(leanpubr)
slug = "biostatmethods"
res = lp_book_info(slug, error = FALSE, verbose = TRUE)
res$content
```
